---
title: "Skin releases and champion balance: general overview"
subtitle: "Construction and exploration of the first analysis cohort"
format:
  html:
    toc: true
    code-fold: true
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
params:
  database: null
  export_csv: true
---

## Objective

The main hypothesis is that champions receive buffs shortly before a skin is released, potentially to increase skin
sales. A secondary question is whether this pattern is stronger for champions that are already popular.

This first report constructs one row per non-base skin release. It is descriptive: because every row is a skin
release, it cannot by itself establish whether buffs are more common than during comparable periods without a skin
release. A later modelling step should add champion-specific control dates and account for repeated releases for the
same champion.

The analysis uses the following conventions:

- skin releases before 2011 are excluded;
- skins marked as cancelled and skins without a release date are excluded;
- skins released from the champion's release date through 60 days afterward are excluded;
- performance is linearly interpolated 30 days before and 14 days after the release date;
- buffs are counted from 42 days before through the release date, including changes shipped on the release date;
- nerfs are counted from the day after release through 42 days after release;
- only buffs and nerfs classified as `CERTAIN` or `VERY_CERTAIN` are counted;
- a skin is excluded if the champion has any classified rework within 60 days on either side of its release;
- multiple skins for the same champion on the same date remain separate rows because the unit is a skin release.

The graph source contains dates but no release times. Interpolation therefore evaluates each target date at midnight
UTC.

## Setup

This report deliberately uses `data.table` and base R graphics rather than the tidyverse.

Install the three required packages once before rendering:

```r
install.packages(c("DBI", "RSQLite", "data.table"))
```

```{r}
#| label: setup
required_packages <- c("DBI", "RSQLite", "data.table")
missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1L), quietly = TRUE)
]

if (length(missing_packages) > 0L) {
  stop(
    "Install the required R packages first: ",
    paste(sprintf("install.packages('%s')", missing_packages), collapse = "; ")
  )
}

library(data.table)

locate_database <- function(configured_path = NULL) {
  candidates <- if (!is.null(configured_path) && nzchar(configured_path)) {
    configured_path
  } else {
    c(
      "data/lol_skin_release_statistics.sqlite3",
      "../../data/lol_skin_release_statistics.sqlite3"
    )
  }
  existing <- candidates[file.exists(candidates)]
  if (length(existing) == 0L) {
    stop("SQLite database not found. Render from the repository root or set params.database.")
  }
  normalizePath(existing[[1L]], mustWork = TRUE)
}

database_path <- locate_database(params$database)
connection <- DBI::dbConnect(
  RSQLite::SQLite(),
  dbname = database_path,
  flags = RSQLite::SQLITE_RO
)

pre_performance_days <- 30L
post_performance_days <- 14L
balance_window_days <- 42L
rework_window_days <- 60L
champion_release_window_days <- 60L
accepted_confidence <- c("CERTAIN", "VERY_CERTAIN")
```

## Read the normalized source tables

`champion_id` below is Riot's stable numeric champion ID. `skin_id` is the Wiki/Riot skin ID rather than the
SQLite surrogate key.

```{r}
#| label: read-data
skins <- as.data.table(DBI::dbGetQuery(connection, "
  SELECT
    champions.game_id AS champion_id,
    champions.name AS champion_name,
    skins.wiki_skin_id AS skin_id,
    skins.display_name AS skin_name,
    skins.release_date AS skin_release_date,
    base_skin.release_date AS champion_release_date
  FROM skins
  JOIN champions ON champions.id = skins.champion_id
  JOIN skins AS base_skin
    ON base_skin.champion_id = champions.id
   AND base_skin.is_base = 1
  WHERE skins.is_base = 0
    AND skins.release_date IS NOT NULL
    AND skins.release_date >= '2011-01-01'
    AND skins.availability <> 'Canceled'
  ORDER BY skins.release_date, champions.name, skins.wiki_skin_id
"))

graph_points <- as.data.table(DBI::dbGetQuery(connection, "
  SELECT
    champions.game_id AS champion_id,
    graph_series.metric,
    graph_points.observed_at_ms,
    graph_points.value
  FROM graph_points
  JOIN graph_series ON graph_series.id = graph_points.graph_series_id
  JOIN champions ON champions.id = graph_series.champion_id
  WHERE graph_series.metric IN ('win_rate', 'popularity')
  ORDER BY champions.game_id, graph_series.metric, graph_points.observed_at_ms
"))

classified_patches <- as.data.table(DBI::dbGetQuery(connection, "
  SELECT
    champions.game_id AS champion_id,
    patch_classifications.patch_id,
    patches.release_date AS patch_release_date,
    patch_classifications.label AS classification_label,
    patch_classifications.confidence
  FROM patch_classifications
  JOIN champions ON champions.id = patch_classifications.champion_id
  JOIN patches ON patches.patch_id = patch_classifications.patch_id
  WHERE patch_classifications.label IN ('buff', 'nerf', 'rework')
"))

DBI::dbDisconnect(connection)

skins[, skin_release_date := as.IDate(skin_release_date)]
skins[, champion_release_date := as.IDate(champion_release_date)]
graph_points[, observed_at_ms := as.numeric(observed_at_ms)]
classified_patches[, patch_release_date := as.IDate(patch_release_date)]
classified_patches[, patch_release_day := as.integer(patch_release_date)]
```

## Interpolate performance around each release

Linear interpolation uses only observations from the same champion and metric. Targets before the first or after the
last available observation remain missing rather than being extrapolated.

```{r}
#| label: interpolate-performance
graph_points[, series_key := paste(champion_id, metric, sep = "::")]
graph_series <- split(
  graph_points[, .(observed_at_ms, value)],
  graph_points$series_key
)

interpolate_value <- function(champion, metric_name, target_date) {
  series <- graph_series[[paste(champion, metric_name, sep = "::")]]
  if (is.null(series) || nrow(series) < 2L) {
    return(NA_real_)
  }

  target_ms <- as.numeric(target_date) * 86400000
  if (target_ms < series$observed_at_ms[[1L]] || target_ms > series$observed_at_ms[[nrow(series)]]) {
    return(NA_real_)
  }

  stats::approx(
    x = series$observed_at_ms,
    y = series$value,
    xout = target_ms,
    method = "linear",
    ties = "ordered",
    rule = 1L
  )$y
}

skin_windows <- copy(skins)
skin_windows[, win_rate_1m_before := mapply(
  function(champion, release_date) {
    interpolate_value(champion, "win_rate", release_date - pre_performance_days)
  },
  champion_id,
  skin_release_date
)]
skin_windows[, win_rate_2w_after := mapply(
  function(champion, release_date) {
    interpolate_value(champion, "win_rate", release_date + post_performance_days)
  },
  champion_id,
  skin_release_date
)]
skin_windows[, popularity_1m_before := mapply(
  function(champion, release_date) {
    interpolate_value(champion, "popularity", release_date - pre_performance_days)
  },
  champion_id,
  skin_release_date
)]
skin_windows[, popularity_2w_after := mapply(
  function(champion, release_date) {
    interpolate_value(champion, "popularity", release_date + post_performance_days)
  },
  champion_id,
  skin_release_date
)]
```

## Count nearby classified patches

Each row is one aggregate classification for a champion in a patch. A champion can therefore contribute at most one
buff or nerf to a given patch window.

```{r}
#| label: balance-windows
classifications_by_champion <- split(classified_patches, classified_patches$champion_id)

count_patch_classifications <- function(champion, target_label, first_date, last_date) {
  classifications <- classifications_by_champion[[as.character(champion)]]
  if (is.null(classifications)) {
    return(0L)
  }

  selected <- classifications[
    classification_label == target_label &
      confidence %chin% accepted_confidence &
      !is.na(patch_release_day) &
      patch_release_day >= as.integer(first_date) &
      patch_release_day <= as.integer(last_date)
  ]
  nrow(selected)
}

skin_windows[, buff_classifications_6w_before := mapply(
  function(champion, release_date) {
    count_patch_classifications(
      champion,
      "buff",
      release_date - balance_window_days,
      release_date
    )
  },
  champion_id,
  skin_release_date
)]
skin_windows[, nerf_classifications_6w_after := mapply(
  function(champion, release_date) {
    count_patch_classifications(
      champion,
      "nerf",
      release_date + 1L,
      release_date + balance_window_days
    )
  },
  champion_id,
  skin_release_date
)]
```

## Exclude releases close to champion releases or reworks

The base skin's release date is the champion release date. A non-base skin launched on that date or during the next
60 days is excluded because newly released champions are generally less stable and always launch with at least one
skin.

The confidence filter is unnecessary for reworks in the current database because every rework classification is
already `CERTAIN` or `VERY_CERTAIN`. The exclusion nevertheless uses all rework labels so it remains conservative if
the classifier is rerun later.

```{r}
#| label: rework-exclusion
rework_dates <- unique(
  classified_patches[
    classification_label == "rework" & !is.na(patch_release_date),
    .(champion_id, patch_release_date)
  ]
)
reworks_by_champion <- split(as.integer(rework_dates$patch_release_date), rework_dates$champion_id)

has_nearby_rework <- function(champion, release_date) {
  dates <- reworks_by_champion[[as.character(champion)]]
  !is.null(dates) && any(abs(dates - as.integer(release_date)) <= rework_window_days)
}

skin_windows[, excluded_for_rework := mapply(
  has_nearby_rework,
  champion_id,
  skin_release_date
)]
skin_windows[, days_since_champion_release := as.integer(
  skin_release_date - champion_release_date
)]
skin_windows[, excluded_for_champion_release :=
  days_since_champion_release >= 0L &
  days_since_champion_release <= champion_release_window_days]
skin_windows[, complete_performance_window := complete.cases(
  win_rate_1m_before,
  win_rate_2w_after,
  popularity_1m_before,
  popularity_2w_after
)]

analysis_data <- skin_windows[
  !excluded_for_champion_release &
    !excluded_for_rework &
    complete_performance_window
]
analysis_data[, `:=`(
  win_rate_change = win_rate_2w_after - win_rate_1m_before,
  popularity_change = popularity_2w_after - popularity_1m_before,
  any_buff_6w_before = buff_classifications_6w_before > 0L,
  any_nerf_6w_after = nerf_classifications_6w_after > 0L,
  release_year = as.integer(format(skin_release_date, "%Y"))
)]
analysis_data[, popularity_percentile := frank(
  popularity_1m_before,
  ties.method = "average"
) / .N]
analysis_data[, popularity_quartile := cut(
  popularity_percentile,
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("Q1: least popular", "Q2", "Q3", "Q4: most popular"),
  include.lowest = TRUE
)]
setorder(analysis_data, skin_release_date, champion_name, skin_id)
```

## Cohort checks and exported matrix

```{r}
#| label: cohort-checks
cohort_flow <- data.table(
  stage = c(
    "Dated, non-base, non-cancelled releases from 2011",
    "After excluding releases within 60 days of champion release",
    "After excluding releases within 60 days of a rework",
    "After requiring all four interpolated measurements"
  ),
  releases = c(
    nrow(skin_windows),
    skin_windows[excluded_for_champion_release == FALSE, .N],
    skin_windows[
      excluded_for_champion_release == FALSE & excluded_for_rework == FALSE,
      .N
    ],
    nrow(analysis_data)
  )
)
print(cohort_flow)

quality_checks <- data.table(
  check = c(
    "Unique champion/skin IDs",
    "Missing requested matrix values",
    "Negative balance-classification counts"
  ),
  failures = c(
    nrow(analysis_data) - uniqueN(analysis_data, by = c("champion_id", "skin_id")),
    sum(!complete.cases(analysis_data[, .(
      champion_id,
      skin_id,
      skin_release_date,
      win_rate_1m_before,
      win_rate_2w_after,
      popularity_1m_before,
      popularity_2w_after,
      buff_classifications_6w_before,
      nerf_classifications_6w_after
    )])),
    analysis_data[
      buff_classifications_6w_before < 0L | nerf_classifications_6w_after < 0L,
      .N
    ]
  )
)
print(quality_checks)

analysis_columns <- c(
  "champion_id",
  "champion_name",
  "skin_id",
  "skin_name",
  "skin_release_date",
  "win_rate_1m_before",
  "win_rate_2w_after",
  "popularity_1m_before",
  "popularity_2w_after",
  "buff_classifications_6w_before",
  "nerf_classifications_6w_after",
  "win_rate_change",
  "popularity_change",
  "any_buff_6w_before",
  "any_nerf_6w_after",
  "popularity_quartile"
)
analysis_matrix <- analysis_data[, ..analysis_columns]
print(head(analysis_matrix, 10L))

if (isTRUE(params$export_csv)) {
  export_directory <- file.path(dirname(database_path), "analysis")
  dir.create(export_directory, recursive = TRUE, showWarnings = FALSE)
  export_path <- file.path(export_directory, "skin_release_matrix.csv")
  fwrite(analysis_matrix, export_path)
  cat("Analysis matrix written to:", export_path, "\n")
}
```

## General buff and nerf statistics

The overall table covers every champion-patch buff and nerf classification in the database regardless of whether a
skin was released nearby. It reports both the complete classified counts and the high-confidence subset used by the
analysis.

```{r}
#| label: general-balance-statistics
overall_balance_statistics <- classified_patches[
  classification_label %chin% c("buff", "nerf"),
  .(
    classified_patches = .N,
    confident_patches = sum(confidence %chin% accepted_confidence),
    confident_share = mean(confidence %chin% accepted_confidence),
    patches_with_known_date = sum(!is.na(patch_release_date)),
    champions = uniqueN(champion_id),
    distinct_patch_ids = uniqueN(patch_id)
  ),
  by = classification_label
]
setorder(overall_balance_statistics, classification_label)
print(overall_balance_statistics)
```

### Baseline by patch year

The yearly baseline is independent of skin releases. It uses patch release dates and the same confidence threshold
as the skin-window counts, making the annual buff/nerf comparison directly relevant to the later analysis. Rows whose
patch has no known release date remain in the overall table above but cannot be assigned to a year.

```{r}
#| label: general-balance-by-year
general_balance_by_year_long <- classified_patches[
  classification_label %chin% c("buff", "nerf") & !is.na(patch_release_date),
  .(
    classified_patches = .N,
    confident_patches = sum(confidence %chin% accepted_confidence)
  ),
  by = .(
    patch_year = as.integer(format(patch_release_date, "%Y")),
    classification_label
  )
]
setorder(general_balance_by_year_long, patch_year, classification_label)
print(general_balance_by_year_long)

general_balance_by_year <- dcast(
  general_balance_by_year_long,
  patch_year ~ classification_label,
  value.var = "confident_patches",
  fill = 0L
)
general_balance_by_year[, `:=`(
  buff_minus_nerf = buff - nerf,
  buff_to_nerf_ratio = fifelse(nerf == 0L, NA_real_, buff / nerf)
)]
print(general_balance_by_year)
```

```{r}
#| label: general-balance-baseline-plots
#| fig-width: 12
#| fig-height: 5.5
old_parameters <- par(mfrow = c(1, 2), mar = c(4.8, 4.2, 2.5, 1))

barplot(
  t(as.matrix(general_balance_by_year[, .(buff, nerf)])),
  beside = TRUE,
  names.arg = general_balance_by_year$patch_year,
  col = c("#6baed6", "#fb6a4a"),
  border = NA,
  las = 2,
  ylab = "Confident champion-patch classifications",
  main = "All buffs and nerfs by patch year"
)
legend(
  "topleft",
  legend = c("Buff", "Nerf"),
  fill = c("#6baed6", "#fb6a4a"),
  border = NA,
  bty = "n"
)

plot(
  general_balance_by_year$patch_year,
  general_balance_by_year$buff_to_nerf_ratio,
  type = "b",
  pch = 16,
  col = "#6a51a3",
  xlab = "Patch year",
  ylab = "Buff classifications / nerf classifications",
  main = "General buff-to-nerf ratio"
)
abline(h = 1, lty = 2, col = "grey35")

par(old_parameters)
```

### Counts in skin-release windows

These counts are conditional on the analysis cohort. Because windows can overlap—and because multiple skins can
share a champion and release date—the totals are counts relative to skin releases rather than unique underlying
champion-patch classifications.

```{r}
#| label: skin-window-balance-statistics

skin_window_balance_statistics <- rbindlist(list(
  analysis_data[, .(
    classification = "buff before release",
    total_classifications = sum(buff_classifications_6w_before),
    mean_classifications_per_release = mean(buff_classifications_6w_before),
    median_classifications_per_release = median(buff_classifications_6w_before),
    maximum_classifications_per_release = max(buff_classifications_6w_before),
    releases_with_at_least_one = sum(any_buff_6w_before),
    share_of_releases_with_at_least_one = mean(any_buff_6w_before)
  )],
  analysis_data[, .(
    classification = "nerf after release",
    total_classifications = sum(nerf_classifications_6w_after),
    mean_classifications_per_release = mean(nerf_classifications_6w_after),
    median_classifications_per_release = median(nerf_classifications_6w_after),
    maximum_classifications_per_release = max(nerf_classifications_6w_after),
    releases_with_at_least_one = sum(any_nerf_6w_after),
    share_of_releases_with_at_least_one = mean(any_nerf_6w_after)
  )]
))
print(skin_window_balance_statistics)
```

## Descriptive overview

```{r}
#| label: descriptive-summary
summary_by_quartile <- analysis_data[, .(
  skin_releases = .N,
  champions = uniqueN(champion_id),
  share_with_buff_before = mean(any_buff_6w_before),
  mean_buff_classifications_before = mean(buff_classifications_6w_before),
  mean_win_rate_change = mean(win_rate_change),
  mean_popularity_change = mean(popularity_change),
  share_with_nerf_after = mean(any_nerf_6w_after)
), by = popularity_quartile]
print(summary_by_quartile)

overall_summary <- analysis_data[, .(
  skin_releases = .N,
  champions = uniqueN(champion_id),
  first_release = min(skin_release_date),
  last_release = max(skin_release_date),
  share_with_buff_before = mean(any_buff_6w_before),
  share_with_nerf_after = mean(any_nerf_6w_after),
  median_win_rate_change = median(win_rate_change),
  median_popularity_change = median(popularity_change)
)]
print(overall_summary)
```

```{r}
#| label: exploratory-plots
#| fig-width: 11
#| fig-height: 9
old_parameters <- par(mfrow = c(2, 2), mar = c(4.2, 4.2, 2.5, 1))

hist(
  analysis_data$buff_classifications_6w_before,
  breaks = seq(-0.5, max(analysis_data$buff_classifications_6w_before) + 0.5, by = 1),
  main = "Buff classifications in the six weeks before release",
  xlab = "Number of confident buff classifications",
  col = "#6baed6",
  border = "white"
)

hist(
  analysis_data$nerf_classifications_6w_after,
  breaks = seq(-0.5, max(analysis_data$nerf_classifications_6w_after) + 0.5, by = 1),
  main = "Nerf classifications in the six weeks after release",
  xlab = "Number of confident nerf classifications",
  col = "#fb6a4a",
  border = "white"
)

quartile_colours <- c("#eff3ff", "#bdd7e7", "#6baed6", "#2171b5")
point_colours <- adjustcolor(
  quartile_colours[as.integer(analysis_data$popularity_quartile)],
  alpha.f = 0.45
)
plot(
  analysis_data$win_rate_1m_before,
  analysis_data$win_rate_2w_after,
  pch = 16,
  col = point_colours,
  xlab = "Win rate 30 days before (%)",
  ylab = "Win rate 14 days after (%)",
  main = "Win rate around skin releases"
)
abline(a = 0, b = 1, lty = 2, col = "grey35")
legend(
  "topleft",
  legend = levels(analysis_data$popularity_quartile),
  col = quartile_colours,
  pch = 16,
  bty = "n",
  cex = 0.8
)

buff_share <- analysis_data[, mean(any_buff_6w_before), by = popularity_quartile]
barplot(
  height = buff_share$V1,
  names.arg = levels(analysis_data$popularity_quartile),
  ylim = c(0, 1),
  col = quartile_colours,
  border = NA,
  las = 2,
  ylab = "Share of skin releases",
  main = "Release preceded by a confident buff"
)

par(old_parameters)
```

## Results by release year

Annual summaries help reveal whether a pooled relationship is driven by a particular period. Years before the graph
history begins do not appear because the cohort requires both pre- and post-release performance measurements. The
latest year may also be incomplete.

```{r}
#| label: yearly-summary
yearly_summary <- analysis_data[, .(
  skin_releases = .N,
  champions = uniqueN(champion_id),
  total_buff_classifications_before = sum(buff_classifications_6w_before),
  total_nerf_classifications_after = sum(nerf_classifications_6w_after),
  share_with_buff_before = mean(any_buff_6w_before),
  share_with_nerf_after = mean(any_nerf_6w_after),
  mean_win_rate_change = mean(win_rate_change),
  mean_popularity_change = mean(popularity_change)
), by = release_year]
setorder(yearly_summary, release_year)
print(yearly_summary)
```

```{r}
#| label: yearly-plots
#| fig-width: 12
#| fig-height: 13
old_parameters <- par(mfrow = c(3, 2), mar = c(4.5, 4.2, 2.5, 1))
year_labels <- yearly_summary$release_year
general_yearly_panel <- general_balance_by_year[match(year_labels, patch_year)]

barplot(
  yearly_summary$skin_releases,
  names.arg = year_labels,
  col = "#74c476",
  border = NA,
  las = 2,
  ylab = "Eligible skin releases",
  main = "Skin releases in the analysis cohort"
)

barplot(
  t(as.matrix(general_yearly_panel[, .(buff, nerf)])),
  beside = TRUE,
  names.arg = year_labels,
  col = c("#6baed6", "#fb6a4a"),
  border = NA,
  las = 2,
  ylab = "Confident champion-patch classifications",
  main = "All buffs and nerfs in each year"
)
legend(
  "topleft",
  legend = c("Buff", "Nerf"),
  fill = c("#6baed6", "#fb6a4a"),
  border = NA,
  bty = "n"
)

barplot(
  rbind(
    yearly_summary$total_buff_classifications_before,
    yearly_summary$total_nerf_classifications_after
  ),
  beside = TRUE,
  names.arg = year_labels,
  col = c("#6baed6", "#fb6a4a"),
  border = NA,
  las = 2,
  ylab = "Classifications across skin-release windows",
  main = "Balance classifications in skin-release windows"
)
legend(
  "topleft",
  legend = c("Buffs before", "Nerfs after"),
  fill = c("#6baed6", "#fb6a4a"),
  border = NA,
  bty = "n"
)

matplot(
  year_labels,
  cbind(
    yearly_summary$share_with_buff_before,
    yearly_summary$share_with_nerf_after
  ),
  type = "b",
  pch = c(16, 17),
  lty = 1,
  col = c("#2171b5", "#cb181d"),
  ylim = c(0, 1),
  xlab = "Skin release year",
  ylab = "Share of skin releases",
  main = "Releases with nearby balance changes"
)
legend(
  "topleft",
  legend = c("Buff before", "Nerf after"),
  col = c("#2171b5", "#cb181d"),
  pch = c(16, 17),
  lty = 1,
  bty = "n"
)

boxplot(
  win_rate_change ~ factor(release_year),
  data = analysis_data,
  outline = FALSE,
  col = "#9ecae1",
  border = "grey35",
  las = 2,
  xlab = "Skin release year",
  ylab = "Percentage-point change",
  main = "Win-rate change by release year"
)
abline(h = 0, lty = 2, col = "grey35")

boxplot(
  popularity_change ~ factor(release_year),
  data = analysis_data,
  outline = FALSE,
  col = "#a1d99b",
  border = "grey35",
  las = 2,
  xlab = "Skin release year",
  ylab = "Percentage-point change",
  main = "Popularity change by release year"
)
abline(h = 0, lty = 2, col = "grey35")

par(old_parameters)
```

```{r}
#| label: yearly-popularity-plot
#| fig-width: 11
#| fig-height: 6
yearly_popularity <- analysis_data[, .(
  share_with_buff_before = mean(any_buff_6w_before),
  skin_releases = .N
), by = .(release_year, popularity_quartile)]
yearly_popularity_wide <- dcast(
  yearly_popularity,
  release_year ~ popularity_quartile,
  value.var = "share_with_buff_before"
)

matplot(
  yearly_popularity_wide$release_year,
  as.matrix(
    yearly_popularity_wide[, setdiff(names(yearly_popularity_wide), "release_year"), with = FALSE]
  ),
  type = "b",
  pch = 15:18,
  lty = 1,
  col = quartile_colours,
  ylim = c(0, 1),
  xlab = "Skin release year",
  ylab = "Share preceded by a confident buff",
  main = "Pre-release buffs by popularity quartile and year"
)
legend(
  "topleft",
  legend = names(yearly_popularity_wide)[-1L],
  col = quartile_colours,
  pch = 15:18,
  lty = 1,
  bty = "n",
  ncol = 2
)
```

## Interpretation and next modelling step

The plots describe what happens around skin releases and whether the descriptive pattern differs with pre-release
popularity. They are not yet a causal test. Calendar time, champion-specific balancing frequency, repeated skins for
the same champion, patch cadence, and general changes in Riot's release practices can all confound the comparison.

A suitable next step is a matched case-control or event-study design. For each real release, sample control dates for
the same champion from periods with sufficient graph coverage and no nearby skin or rework, then compare the
probability or count of preceding buffs. Champion and calendar-period effects can subsequently be included in a
conditional logistic, count, or mixed-effects model.
